\documentclass{article}

\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{multicol}

\setmainfont{Arial}

\author{Luis A. Ramírez García}

\renewcommand{\maketitle}{
  \begin{center}
    {
      \huge\bfseries
      \theauthor{}
    }

    \vspace{1em}

    Zacatecas, Zacatecas 99544 $\bullet$ (+52) 499 100 5287

    \vspace{0.5em}

    tonyramirez.business@outlook.com $\bullet$ linkedin.com/in/tonyramirez1 $\bullet$ github.com/croobat $\bullet$ croobat.com

    \vspace{-0.5em}

  \end{center}
}

\titleformat{\section}
{\huge\bfseries} % formatting
{} % numbering
{0em} % Distance between number and title
{}[\titlerule] % Codigo entre el titulo y el numero

\titleformat{\subsection}
{\bfseries\large}
{\hspace{0in}$\bullet$}
{0.2em}
{}

\titleformat{\subsubsection}
{\bfseries}
{}
{0em}
{}

\titlespacing{\subsubsection}
{0em}
{.5em}
{.5em}

\begin{document}

  \maketitle

  \section{Summary}% {{{

  Mechatronics engineer. Fullstack web developer. Mechatronics engineering graduate with a focus in web development, as well as game development and Linux system administration services.

  \begin{itemize}
    \item Proficient in the process of designing, manufacturing and constructing mechatronics systems, as well as automate industrial processes.

    \item Capable of quickly learning and adapting to new technologies.

    \item Lover of free and open source software as well as global commuications.

    \item Fluent user of the english language.

    \item Believer in discipline and constant self-development.

    \item Ethical and responsible.

    \item Good at googling.
  \end{itemize}% }}}


  \section{Technical skills}% {{{

  \subsection{Programming}

  Git, Github, Linux, Node.js, SQL, APIs, Machine Learning, Data Analysis, Excel. Circuit analysis and design, computing tools, FPGA programming, PLC programming,  hardware programming, machine vision systems, machine learning, fuzzy systems.

    \subsection{Languages}

    \subsubsection{Programming}

    \begin{itemize}
      \item General purpose: C, C++, C\#, Python, GDScript.
      \item Scripting languages: JavaScript, PHP, Lua, Python, Shell.
      \item Hardware description: VHDL, Verilog.
      \item Numerical computing: MATLAB, Python.
      \item Assembly language.
    \end{itemize}

    \subsubsection{Markup}

    HTML5/CSS3, {\LaTeX}, Markdown, XML, JSON\@.

    \subsubsection{Frameworks}

    JQuery, React.js, Vue.js, Node.js, Laravel, Bootstrap, Hugo, Electron.

    \subsubsection{Database management}

    MySQL, MongoDB, SQL Server.

    \subsection{General engineering}
    \begin{itemize}
      \item Mechanical systems: Mechanical design, mechanical CAD, manufacture processes, hydraulics, pneumatics, maintenance of manufacturing systems, fluid mechanics.
      \item Control systems: Logical circuits, sensor conditioning, control o mechatronics systems, industrial automation.
      \item Electronics systems: Digital electronics, analogue electronics, electric machines, power electronics, PCB design, digital signal processing, virtual instrumentation.
    \end{itemize}

    \subsection{Software}

    Microsoft office suite, Adobe suite (particulary Adobe InDesign) VIM, VSCode, Webpack module bundler, Xilinx ISE, Solidworks/FreeCAD, ANSYS, Inkscape, GIMP, Kdenlive, Aseprite, Scilab, OrCAD, FluidSIM, Simatic step7.


  \section{General skills}

  \subsection{Technical skills}
  Mock-ups for printed materials, spreadsheet and slideshow creation, data analysis, image and video edition, vector image and logo design.

  \subsection{Soft skills}
  Verbal communication, teamwork skills, problem-solving, work under pressure, public speaking, decision making, creative, ethical, analytical and profesional.% }}}


  \section{Education}% {{{

  \subsection{Bachelor's degree $\bullet$  Mechatronics engineer $\bullet$ 2022 $\bullet$ 8.8}
  \subsubsection{Instituto Politecnico Nacional.
  Unidad Profesional Interdisciplinaria de Ingenieria campus Zacatecas.
  Zacatecas, Mexico.}% }}}


  \section{Industry experience}% {{{

  \subsection{Lion System Solutions, Aguascalientes, Mexico}

  \subsubsection{Fullstack Web Developer \& System Administrator $\bullet$ (06/2022) \texttt{-} (current)}

  As a PHP Web Developer \& System Administrator, I am responsible for developing, maintaining, and enhancing PHP-based websites using HTML, CSS, JavaScript, jQuery, and Ajax. I also work with Vue and Django in the job. \newline

 I manage databases using MySQL, including designing tables and optimizing queries, and perform system administration tasks on Linux Debian web servers, including setup, configuration, and monitoring. \newline
 
I collaborate with the development team to understand requirements and ensure timely delivery of high-quality projects, and stay up-to-date with the latest developments in web development and system administration, recommending new technologies and best practices.

  \subsection{\textbf{Freelancing}, Zacatecas, Mexico}

  \subsubsection{Open Source Software Contributor $\bullet$ (11/2021) \texttt{-} (Present)}

  Developing various HTML,CSS and JS static sites through GitHub as a solo entrepeneur, as well as participating in game developing jams; developing free software written in GDScript.

  \subsection{Unidad Profesional Interdisciplinaria de Ingenieria campus Zacatecas, Zacatecas, Mexico}

  \subsubsection{Tutoring advisor $\bullet$ (02/2021) \texttt{-} (11/2021)}

  Part of the IPN tutorial program by pairs. Teaching programming languages like C++, MATLAB and VHDL, as well as developing career-related projects.% }}}


  \section{Additional Work Experience}% {{{

  \subsection{\textbf{Lions International}, Zacatecas, Zacatecas}

  \subsubsection{Ambulant vendor$\bullet$ (06/2018) \texttt{-} (03/2019)}

  Sale and distribution of various products, from food to enviroment-friendly products. Ease of speech and dealing with the client.

  \subsection{\textbf{Radiadores Jose's}, Calera de Victor Rosales, Zacatecas}

  \subsubsection{Chief mechanic's assistant $\bullet$ (08/2016) \texttt{-} (03/2017)}

  As a mechanic's assistant, learned to be clean and organized, as well as managing customer oriented tasks. Developing a tolerance to perform repetitive tasks.% }}}


  \section{Certifications}% {{{

  \begin{itemize}
    \item Solidworks Mechanical Design Associate (2021).
    \item Platzi certificated in:

      \begin{multicols}{2}
      \begin{itemize}
        \item Use of Linux developing enviroment.
        \item Theoretical and practical frontend developer.
        \item Theoretical and practical use of HTML and CSS\@.
        \item Profesional Git and GitHub.
        \item Dependency and package management with npm.
        \item Webpack.
        \item Asyncronism with JavaScript.
        \item ECMAScript 6+.
        \item React.js advanced.
        \item PHP practical.
        \item Linux server administration.
        \item SQL practical.
        \item Excel for data analysis.
      \end{itemize}
      \end{multicols}
  \end{itemize}% }}}


  \section{Languages}% {{{

  \begin{itemize}
    \item Spanish.
    \item English.
  \end{itemize}% }}}


  \section{Hobbies}% {{{

  In my free time I enjoy reading, running, programming and learning while contributing to free and open source software. Learning and teaching is my passion.% }}}

\end{document}
