\documentclass{article}

\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=1in]{geometry}

\renewcommand{\maketitle}{
  \begin{center}
    {
      \huge\bfseries
      \theauthor
    }

    \vspace{1em}

    Zacatecas, Zacatecas 99544 - (+52) 499 100 5287

    \vspace{0.5em}

    tonyramirez.busines@outlook.com - linkedin.com/in/tonyramirez1 - github.com/Croobat

  \end{center}
}

\titleformat{\section}
{\huge\bfseries} % formatting
{} % numbering
{0em} % Distance between number and title
{}[\titlerule] % Código entre el título y el numero

\titleformat{\subsection}
{\bfseries\Large}
{$\bullet$}
{0.2em}
{}

\titleformat{\subsubsection}
{\bfseries}
{}
{0em}
{}


\author{Luis Antonio Ramírez García}

\title{Luis A. Ramírez García}

% \subtitle{ Zacatecas, Zacatecas 99544 - (+52) 499 100 5287 tonyramirez.business@outlook.com - linkedin.com/in/tonyramirez1 - github.com/Croobat }

% \author{}
% \date{}

\begin{document}% {{{

  \maketitle

  \section{Summary}

  Recent mechatronics engineering graduate with a focus in Front-end web development, as well as game development and Linux system administration.

  \begin{itemize}
    \item Proficient in the process of designing, manufacturing and constructing mechatronics systems, as well as automate industrial processes.

    \item Capable of quickly learning and adapting to new technologies.

    \item Lover of free and open source software as well as global commuications.

    \item Fluent user of the english language.

    \item Believer in discipline and constant self-development.

    \item Ethical and responsible.
  \end{itemize}


  \section{Technical skills}

  Git, Github, Linux, Node.js, SQL, APIs, Machine Learning, Data Analysis, Excel.

    \subsection{Languages}

    \subsubsection{Programming}

    \begin{itemize}
      \item General purpose: C, C++, C\#, Python, GDScript.
      \item Scripting languages: JavaScript, PHP, Lua, Python, Shell
      \item Hardware description: VHDL, Verilog.
      \item Numerical computing: MATLAB, Python.
      \item Assembly language.
    \end{itemize}

    \subsubsection{Markup}

    HTML5/CSS3, {\LaTeX}, Markdown, XML, JSON.

    \subsubsection{Frameworks}

    JQuery, React.js, Angular, Vue.js, Node.js, Laravel, Django, Bootstrap, Hugo, Electron.

    \subsubsection{Package managers}

    Pacman, npm, yam.

    \subsection{Software}

    Microsoft office suite, VIM, VSCode, Webpack module bundler, Xilinx ISE, Solidworks/FreeCAD, Adobe Illustrator/Inkscape, Adobe Photoshop/GIMP, Kdenlive, Aseprite.


  \section{General skills}

  \subsection{Technical skills}
  Mock-ups for printed materials, spreadsheet and slideshow creation, data analysis, image and video edition, vector image and logo design.

  \subsection{Soft skills}
  Verbal communication, teamwork skills, problem-solving, work under pressure, public speaking, decision making, creative, ethical, analytical and profesional.


  \section{Education}

  Mechatronics engineer, 2022, 8.8

  Instituto Politécnico Nacional; Unidad Profesional Interdisciplinaria de Ingeniería campus Zacatecas, Zacatecas, Mexico.


  \section{Industry experience}

  \subsection{\textbf{Unidad Profesional Interdisciplinaria de Ingeniería Zacatecas}, Zacatecas, Mexico}

  Tutoring advisor

  (02/2021) - (11/2021)

  Part of the IPN tutorial program by pairs. Teaching programming languages like C++, MATLAB and VHDL, as well as developing career-related projects.

  \subsection{\textbf{Freelancing}, Zacatecas, Mexico}

  Open Source Software Contributor

  (11/2021) - Present

  Developing various HTML,CSS and JS static sites through GitHub as a solo entrepeneur, as well as participating in game developing jams; developing free software written in GDScript.


  \section{Additional Work Experience}

  \subsection{\textbf{Freelancing}, Zacatecas, Zacatecas}

  Food deliveryman

  (08/2019) - (03/2020)

  Distributor of self-made "burritos" between college classes.

  \subsection{\textbf{Lions International}, Zacatecas, Zacatecas}

  Ambulant vendor

  (06/2018) - (03/2019)

  Sale and distribution of various products, from food to enviroment-friendly products. Ease of speech and dealing with the client.

  \subsection{\textbf{Radiadores Jose's}, Calera de Victor Rosales, Zacatecas}

  Chief mechanic's assistant

  (08/2016) - (03/2017)

  As a mechanic's assistant, learned to be clean and organized, as well as managing customer oriented tasks. Developing a tolerance to perform repetitive tasks.


  \section{Certifications}

  \begin{itemize}
    \item Solidworks Mechanical Design Associate (2021).
    \item Platzi certificated in:
      \begin{itemize}
        \item Use of Linux developing enviroment.
        \item Theoretical and practical frontend feveloper course.
        \item Javascript course.
        \item Theoretical and practical course of HTML and CSS.
        \item Profesional course of Git and GitHub.
        \item Dependency and package management with npm.
        \item Webpack course.
        \item Asyncronism with JavaScript.
        \item ECMAScript 6+
        \item React.js advanced course.
        \item PHP practical course.
        \item Linux server administration course.
        \item Laravel introductory course.
        \item SQL practical course.
        \item Excel course for data analysis.
      \end{itemize}
  \end{itemize}


  \section{Languages}

  \begin{itemize}
    \item Spanish.
    \item English.
  \end{itemize}


  \section{Hobbies}

  In my free time I enjoy reading, running, programming and learning while contributing to free and open source software. Learning and teaching is my passion.

\end{document}% }}}
